Distributed Topology Discovery in Self-Assembled Nano Networks

### 2014-05-26 trunk/PAPER/implementation.tex
Reviewer comment fixed

All the blocks described above, reacts with the rising edge of
the \emph{clock signal}. An asynchronous system \emph{reset} signal is
also present to restore all registers to their default values. When
this signal is set, DBS state machines for each network
node are set as \emph{Free}.  
Figure~\ref{fig:pipeline} is shows the pipeline structure of the
\disr{} architecture. Packets incoming from neighbor nodes (or
generated locally) are sent to the DBS state machine in order to
ensure the status commutation. While DBS updates its state, in the
next clock cycle the control circuitry will update LED registers status and
will drive the \emph{Switch Matrix} in order to send eventually the packets to
the right output buffer.
%--------------------------------------------------------------------
\subsection{Synthesis results}

@@

Regarding the power consumption of whole \disr{} devices, 
we avoided an accurate power analysis with the switch activity
annotation due to the fact that \disr{} circuitry will be active 
only once during system startup. Indeed, after the setup phase, 
when all segments are mapped, the \disr{} block will stop its activity 
passing all the information related to segments to the routing
algorithm. For this reason the dynamic power falls to zero and
the only consumption could be due to the leakage
consumption.

>>>>

All the blocks described above, reacts with the rising edge of
the \emph{clock signal}. An asynchronous system \emph{reset} signal is
also present to restore all registers to their default values. When
this signal is set, DBS state machines for each network
node are set as \emph{Free}.  
Figure~\ref{fig:pipeline} is shows the pipeline structure of the
\disr{} architecture. Packets incoming from neighbor nodes (or
generated locally) are sent to the DBS state machine in order to
ensure the status commutation. While DBS updates its state, in the
next clock cycle the control circuitry will update LED registers status and
will drive the \emph{Switch Matrix} in order to send eventually the packets to
the right output buffer.
%--------------------------------------------------------------------
\subsection{Synthesis results: Timing, Area and Power consumption considerations}

@@

Regarding the power consumption of whole \disr{} devices, 
we avoided an accurate power analysis with the switch activity
annotation due to the fact that \disr{} circuitry will be active 
only once during system startup. Indeed, after the setup phase, 
when all segments are mapped, the \disr{} block will stop its activity 
passing all the information related to segments to the routing
algorithm. For this reason the dynamic power falls to zero and
the only consumption could be due to the leakage
consumption. Finally with the reported results a coparison between 
RPF configuration circuits and the proposed circuits could be performed.
in particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{Patwardhan_nanoarch06}. In this work, as reported,  the implementation of the RPF requires an overhead of about 1692 CNFET for a $100\times\100$ network. Furthemore, regarding the power consumption, this last implementation require a setup phase beyond which, the consumptions tends to zero. Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.
